---
title: "Untitled"
author: "Justin Vargas"
date: "2022-11-28"
output: github_document
---
---
title: "p8105_nr2774"
output: github_document
---

### Problem 1

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(viridis)
library(dplyr)
library(rvest)
library(purrr)
library(ggplot2)
library(patchwork)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
payroll_df = 
    read_csv("data/Citywide_Payroll_Data__Fiscal_Year_.csv") |> 
    clean_names() |>
    filter(fiscal_year == "2022") |>
    select(-payroll_number, -agency_start_date) |> 
    mutate(pay_basis = recode(pay_basis, "per Annum" = "Annually"),
           pay_basis = recode(pay_basis, "per Day" = "Daily"),
           pay_basis = recode(pay_basis, "per Hour" = "Hourly"),
           leave_status = leave_status_as_of_june_30,
           total_pay = regular_gross_paid + total_ot_paid + total_other_pay) |>
    filter(work_location_borough != "NA",work_location_borough != "OTHER") |> select(-leave_status_as_of_june_30)

#Need to create a new variable for borough and possibly look into removing decimal places for salary, and check NAs in first and last name
```

```{r}
median_total_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      median_total_pay = median(total_pay, na.rm = TRUE)) %>%
        ggplot(aes(x = work_location_borough, y = median_total_pay, fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Median Total Pay",
    title = "The Median Total Pay By County"
  )

median_base_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      median_base_salary = median(base_salary, na.rm = TRUE)) %>%
        ggplot(aes(x = work_location_borough, y = median_base_salary , fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Median Base Salary",
    title = "The Median Base Salary By County"
  )

mean_total_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      mean_total_pay = mean(total_pay, na.rm = TRUE)) %>%
        ggplot(aes(x = work_location_borough, y = mean_total_pay, fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Mean Total Pay",
    title = "The Mean Total Pay By County"
  )

total_ls = table(payroll_df$leave_status)
total_ls

labels = c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal")

piepercent = round(100 * total_ls / sum(total_ls), 1)

pie(total_ls, labels = paste(labels, sep = " ", piepercent, "%"),
    main = "Leave Status Pie Chart", col = rainbow(length(total_ls)))
legend("topright", c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal"),cex = 1, fill = rainbow(length(total_ls)))

library(plotrix)

pie3D(total_ls, labels = piepercent,
    main = "Leave Status Pie Chart", col = rainbow(length(total_ls)))
legend("topright", c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal"),cex = 1, fill = rainbow(length(total_ls)))


Ls_boro = payroll_df %>%
  group_by(work_location_borough, leave_status) %>%
  summarise(
    count = n())
Ls_boro

ggplot(Ls_boro, aes(x = leave_status, y = count, fill = work_location_borough)) + geom_bar(position = "dodge", stat = "identity") + labs(x = "Leave Status", y = "Count")

  # visualizations Number of employees by county separated by leave status
  # Number of agencies separated by county scatterplot Nerugi