---
title: "p8105_final_project"
output: github_document
---

# Loading Libraries 

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
payroll_data = 
    read_csv("data/Citywide_Payroll_Data__Fiscal_Year_.csv") %>% 
    clean_names() %>%
    filter(fiscal_year == "2022",
           work_location_borough != "NA",
           work_location_borough != "OTHER",
           work_location_borough != "WASHINGTON DC",
           leave_status_as_of_june_30 != "ON SEPARATION LEAVE",
           leave_status_as_of_june_30 != "SEASONAL",
           title_description != "NA") %>%
       separate(agency_start_date, into = c("month", "day", "start_year"), convert = TRUE) %>% 
      mutate(leave_status = leave_status_as_of_june_30,
             pay_basis = recode(pay_basis, "per Annum" = "Annually"),
             pay_basis = recode(pay_basis, "per Day" = "Daily"),
             pay_basis = recode(pay_basis, "per Hour" = "Hourly"),
             county_name = work_location_borough,
             county_name = recode(county_name, "MANHATTAN" = "NEW YORK"),
             county_name = recode(county_name, "BROOKLYN" = "KINGS",
             job_title = title_description)) %>% 
    select(-payroll_number, -first_name, -last_name, -mid_init, -month, -day, -leave_status_as_of_june_30, -regular_hours, -ot_hours, -regular_gross_paid, -work_location_borough) %>% 
    mutate(county_name = as.factor(county_name),
           pay_basis = as.factor(pay_basis),
           leave_status = as.factor(leave_status),
           job_title = title_description) %>%
  select(-title_description)

head(payroll_data)
#should agency_name be a factor?
```

# Justin's Visualizations

## First Plot - Mean Base Salary By New York Counties
```{r}
mean_base_salary_plot =
  payroll_data %>%
  group_by(county_name) %>%
  summarize(
      mean_base_salary = mean(base_salary, na.rm = TRUE)) %>%
        ggplot(aes(x = reorder(county_name, mean_base_salary), y = mean_base_salary, fill = county_name)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_y_continuous(
      labels = scales::comma) +
  labs(
    x = "County Names",
    y = "Mean Base Salary",
    title = "The Average Base Salary for Municipal Employees of New York State By County",
    fill = "New York State County Names"
  ) + 
  theme(axis.text.x = element_text(angle = 80, vjust = 0.5, hjust = 0.50)) 

mean_base_salary_plot
```
 
## Second Plot - Total Other Pay by New York Counties

```{r}
median_other_pay_plot =
  payroll_data %>%
        ggplot(aes(x = reorder(county_name, total_other_pay), y = total_other_pay, fill = county_name)) +
  geom_boxplot() +
    scale_y_continuous(
      labels = scales::comma,
    limits = c(-20000, 40000),
    breaks = seq(-20000, 40000, by = 10000)) +
  labs(
    x = "County Names",
    y = "Median Total Other Types of Pay",
    title = "The Median Total Other Pay for Municipal Employees of New York State By County",
    fill = "New York State County Names"
  ) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0.5)) 

median_other_pay_plot
#Fix reordering of boxplots
```


## Third Plot - Total Number of Job Titles by New York Counties

```{r}
number_job_titles_plot =
  payroll_data %>%
  group_by(county_name, job_title) %>%
  summarise(count = n()) %>%
  ungroup() %>% 
  group_by(county_name) %>%
  summarise(count = n()) %>%
        ggplot(aes(x = reorder(county_name, count), y = count, fill = county_name)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_y_continuous(
      labels = scales::comma,
    limits = c(0, 1500),
    breaks = seq(0, 1500, by = 250)) +
  labs(
    x = "County Names",
    y = "Number of Job Titles",
    title = "The Number of Job Titles Held By Municipal Employees of New York State By County",
    fill = "New York State County Names"
  ) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 

number_job_titles_plot
```




# Old Code

```{r}
#Numbers of employees for each leave status

median_total_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      median_total_pay = median(total_pay, na.rm = TRUE)) %>%
        ggplot(aes(x = reorder(work_location_borough, -median_total_pay), y = median_total_pay, fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Median Total Pay",
    title = "The Median Total Pay By County"
  ) + coord_flip()

# Change counties to a factor 
#Arrange from lowest to highest using factors factor reorder 

median_base_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      median_base_salary = median(base_salary, na.rm = TRUE)) %>%
        ggplot(aes(x = reorder(work_location_borough, -median_base_salary_, y = median_base_salary , fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Median Base Salary",
    title = "The Median Base Salary By County"
  )
#consider plotly for the visualizations 

mean_total_df =
  payroll_df %>%
  group_by(work_location_borough) %>%
  summarize(
      mean_total_pay = mean(total_pay, na.rm = TRUE)) %>%
        ggplot(aes(x = work_location_borough, y = mean_total_pay, fill = work_location_borough)) +
  geom_bar(position = "dodge", stat = "identity") +
  labs(
    x = "County Names",
    y = "Mean Total Pay",
    title = "The Mean Total Pay By County"
  )

total_ls = table(payroll_df$leave_status)
total_ls

labels = c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal")

piepercent = round(100 * total_ls / sum(total_ls), 1)

pie(total_ls, labels = paste(labels, sep = " ", piepercent, "%"),
    main = "Leave Status Pie Chart", col = rainbow(length(total_ls)))
legend("topright", c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal"),cex = 1, fill = rainbow(length(total_ls)))

library(plotrix)

pie3D(total_ls, labels = piepercent,
    main = "Leave Status Pie Chart", col = rainbow(length(total_ls)))
legend("topright", c("Active", "Ceased", "On Leave", "On Separation Leave", "Seasonal"),cex = 1, fill = rainbow(length(total_ls)))


Ls_boro = payroll_df %>%
  group_by(work_location_borough, leave_status) %>%
  summarise(
    count = n())

  
Ls_boro

ggplot(Ls_boro, aes(x = leave_status, y = count, fill = work_location_borough)) + geom_bar(position = "dodge", stat = "identity") + labs(x = "Leave Status", y = "Count")






Ls_boro2 = payroll_df %>%
  group_by(work_location_borough, agency_name) %>%
  summarise(
    count = n()) %>% 
  ungroup() %>% 
  group_by(work_location_borough) %>%
  summarise(count = n())

ggplot(Ls_boro2, aes(x = work_location_borough, y = count, fill = work_location_borough)) + geom_bar(position = "dodge", stat = "identity") + labs(x = "Work Location Borough", y = "Count")

  # visualizations Number of employees by county separated by leave status
  # Number of agencies separated by county scatterplot
# number of total ot hours 
#number of other pay


#Things to do



List of things to do:
1. Clean the data (Keep counties and government city, remove Washington) (Group)
2. Visualizations
-Bar Graph for mean base salary by municipality (Justin)
-Bar Graph for number of employees by municipality separated by leave status (Varvara)
-Boxplot for overtime pay by municipality (Nergui)
-Boxplot for total other pay by municipality (Justin)
-Pie Chart for the percentages and numbers of the different leave statuses (Varvara)
-Median base salary by pay basis by county (Nergui)

(Incorprate plotly into each)
3. Do ANOVA and Paired t-test analyses for the mean base salary by municipality (Varvara and Justin)
4. Do the Website (Nergui)
5. Do the Report (Group)
6. Do the Screencast (Group)





